---
title: "Between- & Within- Person Stress Predicts Emotion Regulation Initiation: The Role of Cognitive Resources and Age"
author: "Mengzhe Wei, Tammy English"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: journal
    toc: yes
    toc_float:
      collapsed: true
---

# ECO Stress and ER Choice Analysis
Notes: Started 23 Oct 2024 by Mengzhe Wei to run analysis looking at ER Decisions and strategy selection based on stress. 
Within person (level 1): stress level in EMA, ER need
Between person (level 2): MCI status (young, CN, MCI)
Outcome variables: 
Whether participant chose to influence their emotions; 

```{r setup, echo=FALSE, eval=TRUE, warning=FALSE, message=FALSE}
# Set up packages and upload data. 
rm(list=ls());
options(warnPartialMatchDollar=TRUE);   # safety option
library(lme4); library(knitr); library(RColorBrewer); library (kableExtra);library(correlation); library(tidyverse); library(psych); library(data.table);library(lmerTest);library(performance);library(car);library(gridExtra);library(glmmTMB)
```

## Data Quality Check

### Dataset Cleaning
```{r center, eval=TRUE, echo=FALSE, warning=FALSE, cache=FALSE, message=FALSE}
# Read in dataset
ESM_clean<-fread("ESM_clean.csv")
survey <- fread("ECO_baseline.csv")
data <-ESM_clean %>%
  group_by(PID) %>%
  mutate (Group_code = case_when(Group == 0 ~ -1,  Group == 1 ~ 0, Group == 2 ~ 1),
          Group = factor(Group_code, levels = -1:1, labels = c("YA","CN","MCI")),
          stress_pm = mean(esm_stressed,na.rm=TRUE),
          NA_pm = mean(negemotions, na.rm=TRUE),
          ER_need_pm = mean(esm_wanted_change, na.rm=TRUE),
          control_pm = mean(situation_control,na.rm=TRUE),
          ER_yes_pm = sum(ER_yes,na.rm = TRUE)/ sum(completed==1,na.rm = TRUE),
          distr_pm = ifelse(sum(ER_yes,na.rm = TRUE) > 0, sum(distr_yes,na.rm = TRUE) / sum(ER_yes,na.rm = TRUE), 0),
          min_pm = ifelse(sum(ER_yes,na.rm = TRUE) > 0, sum(min_yes,na.rm = TRUE) / sum(ER_yes,na.rm = TRUE), 0),
          reap_pm = ifelse(sum(ER_yes,na.rm = TRUE) > 0, sum(reap_yes,na.rm = TRUE) / sum(ER_yes,na.rm = TRUE), 0))%>% 
  ungroup()%>%
  mutate(
    stress_gmc = scale(esm_stressed, center = T, scale = F),
    stress_w = esm_stressed - stress_pm,
    stress_b = stress_gmc - stress_w,
    NA_gmc = scale(negemotions, center = T, scale = F),
    NA_w = negemotions - NA_pm,
    NA_b = NA_gmc - NA_w,
    control_gmc = scale(situation_control, center = T, scale = F),
    control_w = situation_control - control_pm,
    control_b = control_gmc - control_w,
    ER_need_gmc = scale (esm_wanted_change, center = T, scale = F),
    ER_need_w = esm_wanted_change -ER_need_pm,
    ER_need_b = ER_need_gmc - ER_need_w,
    CESD_gmc = scale(CES_D_sum, center = T, scale = F)) %>%
  group_by(PID,day) %>%
  mutate(
    stress_lag_w = lag (stress_w,1),
    stress_lag_b =lag (stress_b,1),
    NA_lag_w =lag (NA_w,1),
    NA_lag_b = lag (NA_b,1),
    control_lag_w = lag(control_w,1),
    control_lag_b = lag(control_b,1),
    ER_need_lag_w = lag (ER_need_w,1),
    ER_need_lag_b = lag (ER_need_b,1)
  ) %>%
  ungroup() %>%
  group_by(PID) %>%
  mutate (consecutive_sum = sum(completed == 1 & !is.na(esm_stressed_lag))) %>%
  ungroup() %>%
  as.data.frame()
data_b <- data %>%
  group_by(PID) %>%
  summarise(
    Group_code=first(Group_code),
    Group = first(Group),  # Assuming all entries of a single group per PID are the same
    completed_sum = sum(completed==1,na.rm = TRUE),
    ER_yes_sum = sum(ER_yes,na.rm = TRUE),
    CES_D_sum = first(CES_D_sum),
    stress_pm = first(stress_pm),
    ER_yes_pm = first(ER_yes_pm),
    ER_need_pm = first (ER_need_pm),
    NA_pm = first(NA_pm),
    distr_pm = first(distr_pm),
    min_pm = first(min_pm),
    reap_pm = first(reap_pm),
    CESD_gmc = first(CESD_gmc),
    consecutive_sum = first(consecutive_sum)) %>%
  ungroup() %>%
  as.data.frame()
sum(data_b$ER_yes_sum) # the number of prompts where pt indicated that they've regulated their emotion since the last prompt / 0-1.5 hr ago.
data$Group <- relevel(data$Group, ref="CN")
sum(data$completed == 1 & !is.na(data$esm_stressed_lag)) #data points where we have data for lagged analysis, 5640  is not bad at all
summary(data_b$consecutive_sum)
exclude_PIDs<-data_b$PID[data_b$consecutive_sum <= 5] #excluding 28 pts in this criteria; exlucding 6 in YA, 9 in CN, 13 in MCI
length(exclude_PIDs)
test <- data_b[data_b$consecutive_sum > 5, ]
table(test$Group)
table(data_b$Group)
data_exclude<-data[!data$PID %in% exclude_PIDs,]
unique(data_exclude$PID)
#Get rid of MCI?
```

### Check internal consistency
```{r Internal consistency, eval=TRUE, echo=TRUE, cache=FALSE, warning=FALSE, message=FALSE}
#Check internal consistency
CESD <- select(survey,CES_D_1:CES_D_20)
omega(CESD) #alpha=0.93, omega=0.95
NA.composite <- select (data,c("PID", "esm_stressed","esm_lonely","esm_angry","esm_nervous","esm_fearful","esm_sad","esm_disgusted","esm_sluggish","esm_bored","esm_isolated") )
omegaSem(NA.composite, id = "PID")
```

### Data distribution and Descriptive Stats
```{r distribution,fig.width=10, fig.height=6, eval=TRUE, echo=TRUE, cache=FALSE,warning=FALSE, message=TRUE}
layout(matrix(1:12, 3,4, byrow=TRUE)); 
par(mar = c(2, 2, 2, 1), mgp = c(1.1, 0.2, 0), tcl = -0.3)
#Check distribution of all data; loop through histogram
variables <- c("completed_sum","consecutive_sum", "ER_yes_sum","CES_D_sum", "stress_pm","NA_pm", "ER_need_pm", "ER_yes_pm","distr_pm", "min_pm","reap_pm")
for (vid in 1:length(variables)) { #vid<-3
  hist(data_b[[variables[vid]]], breaks = 20, border = "black",main = variables[vid], xlab = variables[vid], ylab = "Count")
}
par(mfrow = c(1, 1))
# Overall stats including centered variables
describe(data_b)
length(which(data_b$CES_D_sum>=16))
# 67 participants met the cutoff for significant depressive symptomatology
ggplot(data_b, aes(x = consecutive_sum, fill = Group)) + 
  geom_histogram(position = "identity", alpha = 0.5, bins = 30) +
  labs(x = "consecutive_sum", y = "Frequency", title = "Histogram by Group") +
  theme_classic() +
  facet_wrap(~ Group) +  # Create separate plots for each group
  scale_fill_brewer(palette = "Set1")  # Optional: Use a color palette
```

### Demographics
```{r Demo, eval=TRUE, echo=TRUE,cache=FALSE, warning=FALSE, message=FALSE}
#Demo table
demo.sum <- data %>% distinct(PID, .keep_all=TRUE) %>%
  select(PID, Group, Race2_1, Race2_2, Race2_3, Race2_4, Race2_5, Race2_6, Race2_7, 
         Gender, Age)
#Group, 0=young adult, 1=CN older adults, 2=MCI older adult
demo.sum %>%
  count(Group)
#Race
demo.sum %>%
  summarise(
    African_American_Black = mean(Race2_1), 
    American_Indian_Alaskan_Native = mean(Race2_2),
    Asian_Asian_American_Pacific_Islander = mean(Race2_3),
    Middle_Eastern_Arab_American = mean(Race2_4),
    Caucasian_European_American = mean(Race2_5),
    Hispanic_Latino = mean(Race2_6),
    Other = mean(Race2_7)
  )
#Age
demo.sum %>%
  summarise(
    mean_age=mean(Age),
    sd_age=sd(Age),
    min_age=min(Age),
    max_age=max(Age)
  )
#Age group by cognitive group
demo.sum %>%
  group_by(Group) %>%
  summarise(
    mean_age=mean(Age),
    sd_age=sd(Age),
    min_age=min(Age),
    max_age=max(Age)
  )
#Gender
demo.sum %>%
  mutate (Gender = factor(Gender, levels = 0:2, labels = c("male","female","other"))) %>%
  count(Gender)
```

### intraclass correlations of EMA items
```{r EMA cor, echo=TRUE,eval=TRUE,cache=FALSE,warning=F, message=F}
fit_logit <- glmer(ER_yes ~ 1 + (1 | PID), data = data, family = binomial(link = "logit"))
model_performance(fit_logit) 
#ICC = .463,54% variance is within person
fit_logit <- glmer(distr_yes ~ 1 + (1 | PID), data = data, family = binomial(link = "logit"))
model_performance(fit_logit) 
#ICC = 0.464,54% variance is within person
fit_logit <- glmer(min_yes ~ 1 + (1 | PID), data = data, family = binomial(link = "logit"))
model_performance(fit_logit) 
#ICC = 0.435
fit_logit <- glmer(reap_yes ~ 1 + (1 | PID), data = data, family = binomial(link = "logit"))
model_performance(fit_logit) 
#ICC = 0.48
fit0 <- glmer(esm_stressed ~ 1 + (1 | PID), data = data)
model_performance(fit0) 
#ICC = 0.408, 59% variance is within person
```


## Correlations

### Lagged; initiation only
```{r cor, echo=TRUE,eval=TRUE,warning=F, cache=FALSE, message=F}
data$PID<-as.numeric(data$PID)
stats<-statsBy(select(data,c("PID","Group","esm_stressed_lag", "negemotions_lag", "ER_need_lag", "ER_yes")),group="PID")
#between person correlations
stats$rbg #Between-Person Correlation for Raw Scores
stats$pbg #Between-Person Correlation for Person-Mean Centered Scores
#within person correlations
stats$rwg #Within-Person Correlation for Raw Scores
stats$pwg #Within-Person Correlation for Person-Mean Centered Scores

within_person_correlations <- stats$rwg
# Extract the variable names
var_names <- colnames(within_person_correlations)
# Initialize an empty matrix to store p-values
p_value_matrix <- matrix(NA, nrow = length(var_names), ncol = length(var_names))
rownames(p_value_matrix) <- var_names
colnames(p_value_matrix) <- var_names
# Loop through variable pairs and calculate p-values using cor.test
for (i in 1:length(var_names)) {
  for (j in 1:length(var_names)) {
    if (i != j) {  # Avoid calculating for the same variable
      # Handle missing values using na.omit
      valid_data <- na.omit(within_person_correlations[, c(i, j)])
      
      # Only run cor.test if enough valid data is available
      if (nrow(valid_data) > 2) {  # cor.test requires at least 3 observations
        cor_test_result <- cor.test(valid_data[, 1], valid_data[, 2])
        p_value_matrix[i, j] <- cor_test_result$p.value
      } else {
        p_value_matrix[i, j] <- NA  # Not enough data to calculate p-value
      }
    }
  }
}
# View the p-value matrix
print(p_value_matrix)

between_person_correlations <- stats$rbg
# Extract the variable names
var_names <- colnames(between_person_correlations)
# Initialize an empty matrix to store p-values
p_value_matrix <- matrix(NA, nrow = length(var_names), ncol = length(var_names))
rownames(p_value_matrix) <- var_names
colnames(p_value_matrix) <- var_names
# Loop through variable pairs and calculate p-values using cor.test
for (i in 1:length(var_names)) {
  for (j in 1:length(var_names)) {
    if (i != j) {  # Avoid calculating for the same variable
      # Handle missing values using na.omit
      valid_data <- na.omit(between_person_correlations[, c(i, j)])
      
      # Only run cor.test if enough valid data is available
      if (nrow(valid_data) > 2) {  # cor.test requires at least 3 observations
        cor_test_result <- cor.test(valid_data[, 1], valid_data[, 2])
        p_value_matrix[i, j] <- cor_test_result$p.value
      } else {
        p_value_matrix[i, j] <- NA  # Not enough data to calculate p-value
      }
    }
  }
}
# View the p-value matrix
print(p_value_matrix)
```

## Multilevel Modeling

### Stress predicting overall ER use, lagged
```{r StressER,echo=TRUE,eval=TRUE,warning=F, cache=FALSE, message=F}
data_exclude$Group <- relevel(data_exclude$Group, ref="YA")
ER <- glmer(ER_yes ~ stress_lag_w + stress_lag_b + Group + 
                        (1 + stress_lag_w | PID), 
                        family = binomial(link = "logit"),
                        data = data_exclude)
summary(ER)
```

### Control predicting stress & control as a moderator
```{r NAER,echo=TRUE,eval=TRUE,warning=F, cache=FALSE, message=F}
control <- lmer(stress_w~control_w+(1+control_w|PID),data=data_exclude)
summary(control)

control_ER <-glmer(ER_yes ~ control_lag_w +  control_lag_b + (1 + control_lag_w | PID), 
            family = binomial(link = "logit"),
            data = data_exclude,
            control = glmerControl(optimizer = "bobyqa"))
summary(control_ER)

#adding in timing of the prompt
control_ER <-glmer(ER_yes ~ control_lag_w +  stress_lag_w + control_lag_b + stress_lag_b + (1 + control_lag_w + stress_lag_w | PID), 
            family = binomial(link = "logit"),
            data = data_exclude,
            control = glmerControl(optimizer = "bobyqa"))
summary(control_ER)

ER <- glmer(ER_yes ~ stress_lag_w*control_lag_w +  (1 + stress_lag_w + control_lag_w | PID), 
            family = binomial(link = "logit"),
            data = data_exclude,
            control = glmerControl(optimizer = "bobyqa"))
summary(ER) 
```

### NA predicting overall ER use, lagged
```{r NAER,echo=TRUE,eval=TRUE,warning=F, cache=FALSE, message=F}
ER <- glmer(ER_yes ~ stress_lag_w+ stress_lag_b+NA_lag_w + NA_lag_b + Group + 
                        (1 + NA_lag_w | PID), 
                        family = binomial(link = "logit"),
                        data = data_exclude)
summary(ER)

#NA itself is significant, but when stress and NA are in the same model, only stress is significant
```

### Moderation analysis: Group (level 2)
```{r Group mod,echo=TRUE,eval=TRUE,warning=F, cache=FALSE, message=F}
ER <- glmer(ER_yes ~ stress_lag_w*Group + stress_lag_b*Group + 
              (1 + stress_lag_w | PID), 
            family = binomial(link = "logit"),
            data = data_exclude,
            control = glmerControl(optimizer = "bobyqa"))
summary(ER) 

#Younger adults initiate less ER compared to CN older adults when experiencing more stress than normal

ef <- effects::effect(term="stress_lag_w:Group", mod=ER)
efdata<-as.data.frame(ef) #convert the effects list to a data frame
efdata$Group<-as.factor(efdata$Group)
g0w<-ggplot(efdata, aes(x=stress_lag_w, y=fit, color=Group,group=Group)) +
    geom_point() +
    geom_line(size=1.2) +
    geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=Group),alpha=0.3) +
    labs(x= "stress_lag_w", y="ER Use", color="Group", fill="Group") +
    theme_classic() + theme(text=element_text(size=12)) +
    scale_y_continuous(breaks = seq(0, 1, by=0.2), limits=c(0,1)) +
    scale_x_continuous(breaks = seq(-5.5, 6, by=2), limits=c(-5.5, 6))

ER <- glmer(ER_yes ~ NA_lag_w*Group + NA_lag_b*Group + 
              (1 + NA_lag_w | PID), 
            family = binomial(link = "logit"),
            data = data_exclude,
            control = glmerControl(optimizer = "bobyqa"))
summary(ER) 
#same finding
ef <- effects::effect(term="NA_lag_w:Group", mod=ER)
efdata<-as.data.frame(ef) #convert the effects list to a data frame
efdata$Group<-as.factor(efdata$Group)
g1w<-ggplot(efdata, aes(x=NA_lag_w, y=fit, color=Group,group=Group)) +
    geom_point() +
    geom_line(size=1.2) +
    geom_ribbon(aes(ymin=fit-se, ymax=fit+se, fill=Group),alpha=0.3) +
    labs(x= "NA_lag_w", y="ER Use", color="Group", fill="Group") +
    theme_classic() + theme(text=element_text(size=12)) +
    scale_y_continuous(breaks = seq(0, 1, by=0.2), limits=c(0,1)) +
    scale_x_continuous(breaks = seq(-5.5, 6, by=2), limits=c(-5.5, 6))
```

### Moderation analysis: ER need (level 1)
```{r Need mod,echo=TRUE,eval=TRUE,warning=F, cache=FALSE, message=F}
ER <- glmer(ER_yes ~ stress_lag_w*ER_need_gmc_lag + stress_lag_b*ER_need_gmc_lag + 
              (1 + stress_lag_w | PID), 
            family = binomial(link = "logit"),
            data = data,
            control = glmerControl(optimizer = "bobyqa"))
summary(ER) 

ER <- glmer(ER_yes ~ NA_lag_w*ER_need_gmc_lag + NA_lag_b*ER_need_gmc_lag + 
              (1 + NA_lag_w | PID), 
            family = binomial(link = "logit"),
            data = data,
            control = glmerControl(optimizer = "bobyqa"))
summary(ER) 
```


### Moderation Visualization
```{r mod graphs, echo=TRUE, eval=TRUE, fig.width=10, fig.height=8, warning=F, cache=FALSE, message=F}
grid.arrange(g0w,g1w, ncol=2)
```
